---
title: "Data Products Sales Pitch"
author: "Wilson"
date: "November 26, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
data("airquality")
airquality$Ozone[is.na(airquality$Ozone)] = mean(airquality$Ozone, na.rm=TRUE)
airquality$Solar.R[is.na(airquality$Solar.R)] = mean(airquality$Solar.R, na.rm=TRUE)
```

## Problem Statement

This shiny app was created with the intent of allowing users to interact with the air quality dataset with a reactive interface though the app.

## Air Quality Overview

### Preditor

The predictors used in this model are `r names(airquality)[2:6]`.

### Prediction

The predicted variable in this model is `r names(airquality)[1]`.

## Modelling

The model was created using Linear Model (LM).

```{r cars, echo = TRUE, eval=FALSE}
model <- lm(Ozone~., airquality)
```

All other columns besides Ozone are available for manipulation via HTML sliders to determine the predicted result.

## Column Plot

All columns can be plotted against Ozone to determine the relation between the two. An example scatterplot is shown below.

```{r plot}
plot(airquality$Wind,airquality$Ozone)
```

